Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-26 article/article.tex
(+) workload paragraph

TODO : parler de la restriction des groupements de modules

@@

@@

$p_{low}$
$p_{normal}$
$p_{high}$

@@

In an operational context, each reconfiguration raise the workload for
controllers. This trend needs to be considered and a transition cost needs to
be defined for this matter. A transition is (TODO), and the transition cost is
then:
\begin{equation}
  C_{tr}(P_1, P_2) =
  \begin{cases}
    0 & \text{if\,} P_1 = P_2\\
    1 & \text{otherwise}
  \end{cases}
\end{equation}

>>>>

A sector is a group of elementary modules, but in practice only a collection
of sectors are allowed in this model. This collection is referred as the context.
This restriction reflect the fact the shape of a sector needs have a relatively
'nice' shape in order to be easely manageable for a controller.

@@

TODO : meilleur explication des transition

@@

Let us now precise the model established to evaluate a workload metric. The
workload depends on external criteria such as sector and trafic complexity
or humain factors (e.g. controller fatigue, stress). In our model, we assum
that the workload felt by a controller is directly and only related to the trafic
complexity.

The simplest approch considers only the number of aircraft per sector $Nb_{aircraft}$. We
defined two arbitary thresholds, namely $th_{low}$ and $th_{high}$, defining
three zones where the workload is low (resp. normal and high) if $Nb_{aircraft} < th_{low}$
(resp. $th_{low} < Nb_{aircraft} < th_{high}$ and $th_{high} < Nb_{aircraft}$).
Those workload levels are translated to probabilities $p_{low}$, $p_{normal}$ and
$p_{high}$, where $p_{low}(S)$ is the probability that the sector $S$ is underloaded
(resp. balanced and overloaded). In short, for a sector $S$ at time $t$ and $Nb_{aircraft}$:
\begin{equation}
  \begin{cases}
    p_{low}^{S, t} = \mathbb{1}_{[0, th_{low}]}(Nb_{aircraft}) \\
    p_{normal}^{S, t} = \mathbb{1}_{[th_{low}, th_{high}]}(Nb_{aircraft})\\
    p_{high}^{S, t} = \mathbb{1}_{[th_{low}, \infty[}(Nb_{aircraft})
  \end{cases}
\end{equation}
where $\mathbb{1}$ is the indicator function defined by:
\begin{equation}
  \mathbb{1}_{I}(x) = 
  \begin{cases}
    1 & \text{if\,} \quad x \in I\\
    0 & \text{otherwise}
  \end{cases}
\end{equation}

This expression of the workload, expressed in term of probabilities, allow us to
use a more complex model for the workload such as a neural network
(see~\cite{gianazza2010forecasting}). This method learn the probabilities $p_{low}$,
$p_{normal}$ and $p_{high}$ based on parameters including trafic complexity and
sector complexity (e.g. airspace volume).

@@

In an operational context, each reconfiguration raise the workload for
controllers. This trend needs to be considered and a transition cost needs to
be defined for this matter. A transition is (TODO), and the transition cost is
then:
\begin{equation}
  C_{tr}(P_1, P_2) =
  \begin{cases}
    0 & \text{if\,} \quad P_1 = P_2\\
    1 & \text{otherwise}
  \end{cases}
\end{equation}
